A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-16 text/formal-defnition.tex
Revise 3.1 and 3.2.

% \AI{Rename ``type variables'' to ``type-level constants''. }
% \AI{I prefer $\varepsilon$ for the non-empty sequence.}  
We assume the denumerable set of type-level constants, ranged over by
metavariables \(X, Y, Z\), the denumerable set of variables, ranged
over by \(x,y,z\), the denumerable set of constants, ranged over by
\(c\), and the denumerable set of stage variables, ranged over by
\(\alpha, \beta, \gamma\).  The metavariables \(A, B, C\) range over
sequences of stage variables; we write \(\varepsilon\) for the empty
sequence. \LMD is defined by the following grammar:

@@

\begin{align*}
    % \textrm{Type variables}  &   &                          & X,Y,Z                                                                                                      \\
    % \textrm{Variables}       &   &                          & x,y,z                                                                                                      \\
    % \textrm{Stage variables} &   &                          & \alpha,\beta,\gamma                                                                                        \\
    % \textrm{Stage}           &   &                          & A,B,C                                                                                                      \\
    \textrm{Kinds}             &  & K,J,I,H,G                & ::= * \mid \Pi x:\tau.K                                                           \\
    \textrm{Types}             &  & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \\
    %     \textrm{Constants}       &   &                          & c                                                                                                          \\
    \textrm{Terms}             &  & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M                   \\
                               &  &                          & \ \ \ \ \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ A \mid \%_\alpha M        \\
    \textrm{Signature}         &  & \Sigma                   & ::= \emptyset \mid \Sigma, X::K \mid \Sigma, c:\tau                               \\
    \textrm{Type environments} &  & \Gamma                   & ::= \emptyset \mid  \Gamma,x:\tau @A                                              \\
\end{align*}

@@

A kind, which is used to classify types, is either $*$, the kind of
proper types (types that terms inhabit), or $\Pi x\colon\tau.K$, the kind
of type operators that takes $x$ as an argument of type $\tau$ and returns a type
of kind $K$.
% Types
% of terms have kind $*$ and dependent types have $\Pi$-kinds.  For
% example, $\lambda x:\I.x$ has type $\Pi x:\I.\I$, which has $*$ kind.
% \red{この段落は短いので型の段落と結合するか?}
% Types
A type is a type-level constant $X$, which is declared in the signature with its kind, a dependent function type $\Pi x:\tau_1.\tau_2$,
an application of a term to a type (operator) of $\Pi$-kind, a code type $\TW_\alpha$, or an $\alpha$-closed type $\F\alpha.\tau$.
An application of a term to a type (operator) of $\Pi$-kind is, for example, $\text{Vector}\ 10$
if type-level constant $\text{Vector}$ has the kind $\Pi x:\I.*$.
A code type $\TW_\alpha \tau$ denotes a code fragment of a term of type $\tau$.
An $\alpha$-closed type corresponds to a runnable code fragment.

% Type constructors tie strongly \AI{Is ``tie strongly'' standard?} in the order of 
An application of a term to a type (operator) of $\Pi$-kind: $\tau\ M$ connect tighter than
the type constructor $\TW_{\alpha}$ and $\TW_{\alpha}$ connect tighter than
$\Pi$ in dependent types such as $\Pi x:\tau.\tau$ and $\Pi$ connect tighter than
$\F$ in types for stage abstraction such as $\F\alpha.\tau$.
Therefore, $\F\alpha.\TW_{\alpha} \Pi x:\I.\text{Vector}\ 5$ is interpreted as
$\F\alpha.(\TW_{\alpha} (\Pi x:\I.(\text{Vector}\ 5)))$.
% \AI{I don't understand this rule...}

@@

Terms include ordinary (explicitly typed) \(\lambda\)-terms, constants,
whose type is declared in signature $\Sigma$, and the following five forms
related to multi-stage programming:
$\TB_\alpha M$ represents a code fragment; $\TB_\alpha M$ represents escape;
$\Lambda\alpha.M$ is a stage variable abstraction;
$M\ A$ is an application of stage $A$ to a stage abstraction; and
$\%_\alpha M$ is an operator for cross-stage persistence.
The prefix operators $\TB_\alpha, \TBL_\alpha$, and $\%_\alpha$ connect tighter than the two forms of applications
and applications are left-associative
and two abstractions extends as far to the right as possible.
For example, $\F\alpha.\lambda x:\I.\TB_\alpha x\ y$ means $\F\alpha.(\lambda x:\I.(\TB_\alpha x)\ y)$.
% \AI{I think the usage of ``application'' is wrong again}

@@

We adopt a \LLF-like system, where constants and type-level constants are given in the signature $\Sigma$, which
are a sequence of declarations of the form $c:\tau$ and $X:K$.
For example, when we use integers in \LMD, $\Sigma = \B :: *, \textrm{true}:\B, \textrm{false}:\B$.
Please note that constants or type-level constants have no stage.
This means that we can use them at any stage.
% Type environments
Type environments are sequences of triples of a variable, its type, and its stage.
We define well-formed signature and well-formed type environments later.

% Free variables
As usual, the variable $x$ is bound in $\lambda x:\tau.M$ or $\Pi x:\tau.\tau$ and
and the stage variable $\alpha$ is bound in $\Lambda \alpha.M$ or $\F\alpha.\tau$.
We sometimes abbreviate $\Pi x:\tau_1.\tau_2$ to $\tau_1 \rightarrow \tau_2$ if
$x$ is not a free variable in $\tau_2$.
We identify $\alpha$-convertible terms and assume the names of bound variables are pairwise distinct.
We write $\FV(M)$ and $\FTV(M)$ for the set of free variables and the set of free stage variables in $M$, respectively.
% \AI{This should be mentioned after free variables are introduced.}
% \AI{What about other binders such as $\Pi$?}

% \AI{We should note that constants and type-level constants are not staged.}
% \paragraph{Remark:}  \AI{

% Comparison with Hanada--Igarashi

As the end of this subsection, we compare \LMD and \LTP.
Terms of \LMD are the same with \LTP except for constants.
The difference between \LMD and \LTP is their types and kinds.
First, \LMD contains $\Pi$ type instead of function type in \LTP.
Second, there two kinds of $\F$ in \LTP in order to discuss on program residualization
although \LMD contains only one $\F$ type.
Third, \LMD contains kinding and type equivalence rules to handle dependent types.

@@

Next, we define the full reduction for \LMD.
Before giving the definition of reduction, we define six kinds of substitutions.
Substitution $M[x\mapsto N], \tau[x \mapsto N]$ and $K[x \mapsto N]$ are
the ordinary capture-avoiding substitutions of
term $N$ for $x$ in term $M$, type $\tau$, and kind $K$, respectively
and we omit their definition here.
Substitution $M[\alpha \mapsto A], \tau [\alpha \mapsto A], K[\alpha \mapsto A]$ and $B[\alpha\mapsto A]$ are
substitutions of stage $A$ for stage variable $\alpha$ in
term $N$ for $x$ in term $M$, type $\tau$, kind $K$, and stage $B$ respectively.
We show replesentive cases below.
% \AI{What about $\tau[x \mapsto N], K[x \mapsto N], \tau [\alpha \mapsto \varepsilon]$ and $K[\alpha \mapsto \varepsilon]$?}

% \AI{Since we always substitute $\varepsilon$ for stage variables, we may want to introduce a special notation, something like $\textit{erase}_\alpha(M)$.}
% \AI{We will use $[\alpha \mapsto \varepsilon]$ and $[\alpha \mapsto \beta]$.  The latter is renaming, so we can omit the definition.}

\begin{align*}
    (\lambda x:\tau.M)[\alpha \mapsto A] & = \lambda x:(\tau[\alpha \mapsto A]).(M[\alpha \mapsto A])                                  \\
    (M\ B)[\alpha \mapsto A]             & = (M[\alpha \mapsto A])\ B[\alpha\mapsto A]                                                 \\
    (\TB_\beta M)[\alpha \mapsto A]      & = \TB_{\beta[\alpha \mapsto A]}M[\alpha \mapsto A]                                          \\
    (\TBL_\beta M)[\alpha \mapsto A]     & = \TBL_{\beta[\alpha \mapsto A]}M[\alpha \mapsto A]                                         \\
    (\%_\beta M)[\alpha \mapsto A]       & = \%_{\beta[\alpha \mapsto A]}M[\alpha \mapsto A]                                           \\
    (\beta B)[\alpha \mapsto A]          & = \beta (B[\alpha\mapsto A])                               & (\text{if } \alpha \neq \beta) \\
    (\beta B)[\alpha \mapsto A]          & = A (B[\alpha\mapsto A])                                   & (\text{if } \alpha = \beta)
\end{align*}

\begin{definition}[Reduction]
    The relations $M \longrightarrow_\beta N$, $M \longrightarrow_\blacklozenge N$, and $M \longrightarrow_\Lambda N$
    are the least compatible relations closed under the rules below.
    Congruence rules which are omitted from the definition.
    \begin{align*}
         & (\lambda x:\tau.M) N \longrightarrow_\beta M[x \mapsto N]         \\
         & \TBL_\alpha \TB_\alpha M \longrightarrow_\blacklozenge M          \\
         & (\Lambda \alpha.M)\ A \longrightarrow_\Lambda M[\alpha \mapsto A]
    \end{align*}
    We write $ M \longrightarrow M'$ iff $ M \longrightarrow_\beta M'$, $ M \longrightarrow_\blacklozenge M'$, or $ M \longrightarrow_\Lambda M'$ and
    we call $\longrightarrow_\beta$, $\longrightarrow_\blacklozenge$, and $\longrightarrow_\Lambda$ $\beta$-reduction, $\blacklozenge$-reduction, and $\Lambda$-reduction, respectively.
\end{definition}

The relation $\longrightarrow_\beta$ represents ordinary $\beta-$reduction in the \(\lambda\)-calculus; the relation
$\longrightarrow_\blacklozenge$ represents that quotation $\TB_\alpha M$ is canceled by escape and $M$ is spliced into the code fragment surrounding the escape;
the relation $\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\varepsilon$ reduces to the body of the abstraction
where $\varepsilon$ is substituted for the stage variable.
There is no reduction rule for CSP as with Hanada and Igarashi \cite{Hanada2014}.
The CSP operator $\%_\alpha$ disappears when $\varepsilon$ is substituted to $\alpha$.
We show an example of a reduction sequence below.
Underlines show the redexes.
\begin{align*}
     & \hspace{10mm} \underline{(\lambda i:\I\to\I.(\Lambda\alpha.\TB_\alpha (\%_\alpha i\ 1 + (\TBL_\alpha \TB_\alpha 3))\ \varepsilon))\ (\lambda x:\I.x)} \\
     & \longrightarrow_\blacklozenge (\Lambda\alpha.\TB_\alpha (\%_\alpha (\lambda x:\I.x)\ 1 + (\underline{\TBL_\alpha \TB_\alpha 3})))\ \varepsilon        \\
     & \longrightarrow_\beta \underline{(\Lambda\alpha.\TB_\alpha (\%_\alpha (\lambda x:\I.x)\ 1 + 3))\ \varepsilon}                                         \\
     & \longrightarrow_\Lambda \underline{(\lambda x:\I.x)\ 1} + 3                                                                                           \\
     & \longrightarrow_\beta 1 + 3                                                                                                                           \\
     & \longrightarrow^* 4
\end{align*}

@@

% 総論

In this section, we define the type system of \LMD.
% \LMD is little complicated because it contains dependent types.
It consists of six judgment forms for typing, kinding, well-formed kinding, term equivalence, type equivalence, and kind equivalence.
We list the judgments forms in Figure~\ref{fig:LMD-six-judgments}.
% \AI{equality vs. equivalence?} \red{Select equivalence}
% \AI{A few judgment forms do not match rules.}

@@

% \AI{Insert a tilde (which is a space without a line break) between ``Figure'' and ref.}
\begin{definition}[Typing, Kinding, Well-formed Kinding, Term Equivalence, Type Equivalence, Kind Equivalence]
    The typing relation $ \G \V M : \tau @ A $,
    the kinding relation $\G \V \tau :: K @ A$,
    the well-formed kinding relation $\G \V K \iskind @ A$,
    the term equivalence relation $\G \V M \E N @ A$,
    the type equivalence relation $\G \V \tau \E \sigma @ A$,
    the kind equivalence relation $\G \V K \E J @ A$,
    are the least relation closed under the rules in Figure~\ref{fig:typing-rules}.
\end{definition}
This definition is little complicated to define six relations at the same time.
We can't define them one by one because they are dependent on each other.

>>>>

We assume the denumerable set of \emph{type-level constants}, ranged over by
metavariables \(X, Y, Z\), the denumerable set of \emph{variables}, ranged
over by \(x,y,z\), the denumerable set of \emph{constants}, ranged over by
\(c\), and the denumerable set of \emph{stage variables}, ranged over by
\(\alpha, \beta, \gamma\).  The metavariables \(A, B, C\) range over
sequences of stage variables; we write \(\varepsilon\) for the empty
sequence. \LMD is defined by the following grammar:

@@

\begin{align*}
    % \textrm{Type variables}  &   &                          & X,Y,Z                                                                                                      \\
    % \textrm{Variables}       &   &                          & x,y,z                                                                                                      \\
    % \textrm{Stage variables} &   &                          & \alpha,\beta,\gamma                                                                                        \\
    % \textrm{Stage}           &   &                          & A,B,C                                                                                                      \\
    \textrm{kinds}             &  & K,J,I,H,G                & ::= * \mid \Pi x:\tau.K                                                           \\
    \textrm{types}             &  & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \\
    %     \textrm{Constants}       &   &                          & c                                                                                                          \\
    \textrm{terms}             &  & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M                   \\
                               &  &                          & \ \ \ \ \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ A \mid \%_\alpha M        \\
    \textrm{signatures}         &  & \Sigma                   & ::= \emptyset \mid \Sigma, X::K \mid \Sigma, c:\tau                               \\
    \textrm{type environments} &  & \Gamma                   & ::= \emptyset \mid  \Gamma,x:\tau @A                                              \\
\end{align*}

@@

A kind, which is used to classify types, is either $*$, the kind of
proper types (types that terms inhabit), or $\Pi x\colon\tau.K$, the kind
of type operators that takes $x$ as an argument of type $\tau$ and returns a type
of kind $K$.
% Types
% of terms have kind $*$ and dependent types have $\Pi$-kinds.  For
% example, $\lambda x:\I.x$ has type $\Pi x:\I.\I$, which has $*$ kind.
% \red{この段落は短いので型の段落と結合するか?}
% Types
A type is a type-level constant $X$, which is declared in the signature with its kind, a dependent function type $\Pi x:\tau_1.\tau_2$,
an application $\tau\ M$ of a type (operator) (of $\Pi$-kind) to a term, a code type $\TW_\alpha$, or an $\alpha$-closed type $\F\alpha.\tau$.
An application of a type (operator) of $\Pi$-kind to a term is, for example, $\text{Vector}\ 10$
if type-level constant $\text{Vector}$ has the kind $\Pi x:\I.*$.
A code type $\TW_\alpha \tau$ is for a code fragment of a term of type $\tau$.
An $\alpha$-closed type corresponds to a runnable code fragment.

% An application $\tau\ M$ of a type (operator) to a term connects tighter than
% $\TW_{\alpha}$ connects tighter than
% $\Pi$ in dependent types such as $\Pi x:\tau.\tau$ and $\Pi$ connect tighter than
% $\F$ in types for stage abstraction such as $\F\alpha.\tau$.
% Therefore, $\F\alpha.\TW_{\alpha} \Pi x:\I.\text{Vector}\ 5$ is interpreted as
% $\F\alpha.(\TW_{\alpha} (\Pi x:\I.(\text{Vector}\ 5)))$.
% \AI{I don't understand this rule...}

@@

Terms include ordinary (explicitly typed) \(\lambda\)-terms, constants,
whose type is declared in signature $\Sigma$, and the following five forms
related to multi-stage programming:
$\TB_\alpha M$ represents a code fragment; $\TB_\alpha M$ represents escape;
$\Lambda\alpha.M$ is a stage variable abstraction;
$M\ A$ is an application of stage $A$ to a stage abstraction; and
$\%_\alpha M$ is an operator for cross-stage persistence.

@@

We adopt the tradition of \LLF-like systems, where types of constants and kinds of type-level constants are globally declared in a signature $\Sigma$, which
is a sequence of declarations of the form $c:\tau$ and $X:K$.
For example, when we use Boolean in \LMD, $\Sigma$ includes $\B :: *, \textrm{true}:\B, \textrm{false}:\B$.
Note that constants and type-level constants are not associated with stages;
so, we can use them at any stage.
% Type environments
Type environments are sequences of triples of a variable, its type, and its stage.
We define well-formed signature and well-formed type environments later.

The variable $x$ is bound in $M$ of $\lambda x:\tau.M$ and in $\tau_2$
of $\Pi x:\tau_1.\tau_2$, as usual; the stage variable $\alpha$ is
bound in $M$ of $\Lambda \alpha.M$ and $\tau$ of $\F\alpha.\tau$.
We write $\FV(M)$ and $\FTV(M)$ for the set of free variables and the set of free stage variables in $M$, respectively.  Similarly, $\FV(\tau)$, $\FTV(\tau)$,
$\FV(K)$, and $\FTV(K)$ are defined.
We sometimes abbreviate $\Pi x:\tau_1.\tau_2$ to $\tau_1 \rightarrow \tau_2$ if
$x$ is not a free variable in $\tau_2$.
% Free variables
We identify $\alpha$-convertible terms and assume the names of bound variables are pairwise distinct.
% \AI{This should be mentioned after free variables are introduced.}
% \AI{What about other binders such as $\Pi$?}

The prefix operators $\TW_\alpha, \TB_\alpha, \TBL_\alpha$, and
$\%_\alpha$ connect tighter than the three forms $\tau\ M$, $M\ N$,
$M\ A$ of applications, which are left-associative; The binders $\Pi$,
$\forall$, and $\lambda$ extend as far to the right as possible.
Thus, $\F\alpha.\TW_{\alpha} (\Pi x:\I.\text{Vector}\ 5)$ is
interpreted as
$\F\alpha.(\TW_{\alpha} (\Pi x:\I.(\text{Vector}\ 5)))$; and
$\Lambda\alpha.\lambda x:\I.\TB_\alpha x\ y$ means
$\Lambda\alpha.(\lambda x:\I.(\TB_\alpha x)\ y)$.

\paragraph{Remark:} Basically, we define \LMD to be an extension of
\LTP with dependent types.  One notable difference is that \LMD has
only one kind of \(\alpha\)-closed types, whereas \LTP has two kinds
of \(\alpha\)-closed types \(\forall\alpha.\tau\) and
\(\forall^\varepsilon\alpha.\tau\).  We have omitted the first kind,
for simplicity, and dropped the superscript $\varepsilon$.  It would
not be difficult to recover the distinction to show properties related
to program residualization~\cite{Hanada2014}.

@@

Next, we define full reduction for \LMD.
Before giving the definition of reduction, we define six kinds of substitutions.
Substitution $M[x\mapsto N], \tau[x \mapsto N]$ and $K[x \mapsto N]$ are
ordinary capture-avoiding substitution of
term $N$ for $x$ in term $M$, type $\tau$, and kind $K$, respectively,
and we omit their definitions here.
Substitution $M[\alpha \mapsto A], \tau [\alpha \mapsto A], K[\alpha \mapsto A]$ and $B[\alpha\mapsto A]$ are
substitutions of stage $A$ for stage variable $\alpha$ in
term $N$ for $x$ in term $M$, type $\tau$, kind $K$, and stage $B$, respectively.
We show representative cases below.
%
\begin{align*}
    (\lambda x:\tau.M)[\alpha \mapsto A] & = \lambda x:(\tau[\alpha \mapsto A]).(M[\alpha \mapsto A])                                  \\
    (M\ B)[\alpha \mapsto A]             & = (M[\alpha \mapsto A])\ B[\alpha\mapsto A]                                                 \\
    (\TB_\beta M)[\alpha \mapsto A]      & = \TB_{\beta[\alpha \mapsto A]}M[\alpha \mapsto A]                                          \\
    (\TBL_\beta M)[\alpha \mapsto A]     & = \TBL_{\beta[\alpha \mapsto A]}M[\alpha \mapsto A]                                         \\
    (\%_\beta M)[\alpha \mapsto A]       & = \%_{\beta[\alpha \mapsto A]}M[\alpha \mapsto A]                                           \\
    (\beta B)[\alpha \mapsto A]          & = \beta (B[\alpha\mapsto A])                               & (\text{if } \alpha \neq \beta) \\
    (\beta B)[\alpha \mapsto A]          & = A (B[\alpha\mapsto A])                                   & (\text{if } \alpha = \beta)
\end{align*}
Here, $\TB_{\alpha_1\cdots\alpha_n} M$,
$\TBL_{\alpha_1\cdots\alpha_n} M$, and $\%_{\alpha_1\cdots\alpha_n} M$
$(n \geq 0)$ stand for $\TB_{\alpha_1} \cdots \TB_{\alpha_n} M$,
$\TBL_{\alpha_1}\cdots \TBL_{\alpha_n} M$, and
$\%_{\alpha_1}\cdots \%_{\alpha_n} M$, respectively.  In particular,
$\TB_{\varepsilon} M = \TBL_{\varepsilon} M = \%_{\varepsilon} M = M$.

\begin{definition}[Reduction]
    The relations $M \longrightarrow_\beta N$, $M \longrightarrow_\blacklozenge N$, and $M \longrightarrow_\Lambda N$
    are the least compatible relations closed under the rules below.
%    Congruence rules are omitted from the definition.
    \begin{align*}
         (\lambda x:\tau.M) N & \longrightarrow_\beta M[x \mapsto N]         \\
         \TBL_\alpha \TB_\alpha M & \longrightarrow_\blacklozenge M          \\
         (\Lambda \alpha.M)\ A & \longrightarrow_\Lambda M[\alpha \mapsto A]
    \end{align*}
\end{definition}
We write $ M \longrightarrow M'$ iff $ M \longrightarrow_\beta M'$,
$ M \longrightarrow_\blacklozenge M'$, or
$ M \longrightarrow_\Lambda M'$ and we call $\longrightarrow_\beta$,
$\longrightarrow_\blacklozenge$, and $\longrightarrow_\Lambda$
$\beta$-reduction, $\blacklozenge$-reduction, and $\Lambda$-reduction,
respectively.
\AI{Don't we need to define $\longrightarrow^*$?}

The relation $\longrightarrow_\beta$ represents ordinary $\beta$-reduction in the \(\lambda\)-calculus; the relation
$\longrightarrow_\blacklozenge$ represents that quotation $\TB_\alpha M$ is canceled by escape and $M$ is spliced into the code fragment surrounding the escape;
the relation $\longrightarrow_\Lambda$ means that a stage abstraction applied to  stage $A$ reduces to the body of the abstraction
where $A$ is substituted for the stage variable.
There is no reduction rule for CSP as with Hanada and Igarashi \cite{Hanada2014}.
The CSP operator $\%_\alpha$ disappears when $\varepsilon$ is substituted for $\alpha$.
We show an example of a reduction sequence below.
Underlines show the redexes.
\begin{align*}
     & \hspace{10mm} \underline{(\lambda i:\I\to\I.(\Lambda\alpha.\TB_\alpha (\%_\alpha i\ 1 + (\TBL_\alpha \TB_\alpha 3))\ \varepsilon))\ (\lambda x:\I.x)} \\
     & \longrightarrow_\blacklozenge (\Lambda\alpha.\TB_\alpha (\%_\alpha (\lambda x:\I.x)\ 1 + (\underline{\TBL_\alpha \TB_\alpha 3})))\ \varepsilon        \\
     & \longrightarrow_\beta \underline{(\Lambda\alpha.\TB_\alpha (\%_\alpha (\lambda x:\I.x)\ 1 + 3))\ \varepsilon}                                         \\
     & \longrightarrow_\Lambda \underline{(\lambda x:\I.x)\ 1} + 3                                                                                           \\
     & \longrightarrow_\beta 1 + 3                                                                                                                           \\
     & \longrightarrow^* 4
\end{align*}

@@

In this section, we define the type system of \LMD.
It consists of six judgment forms for typing, kinding, well-formed kinding, term equivalence, type equivalence, and kind equivalence.
We list the judgments forms in Figure~\ref{fig:LMD-six-judgments}.

@@

\begin{definition}[Typing, Kinding, Well-formed Kinding, Term Equivalence, Type Equivalence, Kind Equivalence]
    The typing relation $ \G \V M : \tau @ A $,
    the kinding relation $\G \V \tau :: K @ A$,
    the well-formed kinding relation $\G \V K \iskind @ A$,
    the term equivalence relation $\G \V M \E N @ A$,
    the type equivalence relation $\G \V \tau \E \sigma @ A$,
    the kind equivalence relation $\G \V K \E J @ A$,
    are the least relation closed under the rules in Figure~\ref{fig:typing-rules}.  \AI{There are more rules!  Some of them are not even in the paper.}
\end{definition}
This definition is little complicated to define six relations at the same time.
We can't define them one by one because they are dependent on each other.
\AI{I think well-formed signatures and type environments cannot be defined independently.}
